Covering Your Basis: Model Agnostic Probes of the Binary Black Hole Population

### 2022-09-26 src/tex/results.tex
add chieff results

\subsection{BBH Mass Distibution} \label{sec:mass_dist}

@@

\subsection{BBH Component Spin Distributions} \label{sec:spin_dist}

@@

Now we model each of the components' orientation distributions with independent \textsc{MSpline} models as done above, and show the inferred 
distributions in figure \ref{fig:ind_spintilt_dist}. The primary and secondary orientation distibutions do not agree as well as the magnitude 
distibutions did in figure \ref{fig:ind_spinmag_dist}, and the PPDs look to peak at different values, but the wide uncertainties still are 
consistent with both each other and the \textsc{Default} model's PPD. We find the two distributions to peak at: $\cos{\theta_1}=$\result{$\CIPlusMinus{\macros[MSplineIndependentCompSpins][peakCosTilt1]}$} 
and $\cos{\theta_2}=$\result{$\CIPlusMinus{\macros[MSplineIndependentCompSpins][peakCosTilt2]}$}, showing that the primary distribution peak is inferred further away 
from the assumed $\cos{\theta}=1$ with the \textsc{Default} model. There is also significant (albeit uncertain) evidence of spin mis-alignments in each distribution, finding 
the fraction of mis-aligned primary and secondary components as: $f_{1,<0}=$\result{$\CIPlusMinus{\macros[MSplineIndependentCompSpins][negFrac1]}$} andand $f_{2,<0}=$\result{$\CIPlusMinus{\macros[MSplineIndependentCompSpins][negFrac2]}$}.
We again calculate the isotropy ratio, Y, for each and find: $\log_{10}Y_1=$\result{$\CIPlusMinus{\macros[MSplineIndependentCompSpins][log10gammaFrac1]}$} and 
$\log_{10}Y_2=$\result{$\CIPlusMinus{\macros[MSplineIndependentCompSpins][log10gammaFrac2]}$}.

@@

Transform comp spin results to effective dims to see how strong changes in mag/tilt dont significantly affect our best constrained/measured
effective spins

Default: $f_{\chi_\mathrm{eff}<-0.3} = $\result{$\CIPlusMinus{\macros[ChiEffective][default][FracBelowNeg0p3]}$} 
    $f_{\chi_\mathrm{eff}<0} = $\result{$\CIPlusMinus{\macros[ChiEffective][default][FracBelow0]}$} 
    $\chi_\mathrm{eff, peak} = $\result{$\CIPlusMinus{\macros[ChiEffective][default][PeakChiEff]}$}

MSplineIID: $f_{\chi_\mathrm{eff}<-0.3} = $\result{$\CIPlusMinus{\macros[ChiEffective][iid][FracBelowNeg0p3]}$}
   $f_{\chi_\mathrm{eff}<0} = $\result{$\CIPlusMinus{\macros[ChiEffective][iid][FracBelow0]}$} 
   $\chi_\mathrm{eff, peak} = $\result{$\CIPlusMinus{\macros[ChiEffective][iid][PeakChiEff]}$}

MSplineIND: $f_{\chi_\mathrm{eff}<-0.3} = $\result{$\CIPlusMinus{\macros[ChiEffective][ind][FracBelowNeg0p3]}$}
   $f_{\chi_\mathrm{eff}<0} = $\result{$\CIPlusMinus{\macros[ChiEffective][ind][FracBelow0]}$} 
   $\chi_\mathrm{eff, peak} = $\result{$\CIPlusMinus{\macros[ChiEffective][ind][PeakChiEff]}$}

MSplineChiEff: $f_{\chi_\mathrm{eff}<-0.3} = $\result{$\CIPlusMinus{\macros[ChiEffective][chieff][FracBelowNeg0p3]}$}
    $f_{\chi_\mathrm{eff}<0} = $\result{$\CIPlusMinus{\macros[ChiEffective][chieff][FracBelow0]}$} 
    $\chi_\mathrm{eff, peak} = $\result{$\CIPlusMinus{\macros[ChiEffective][chieff][PeakChiEff]}$}

Present results fitting chi eff dist with MSpline I am making a change.

>>>>

\subsection{Binary Black Hole Masses} \label{sec:mass_dist}

@@

\subsection{Binary Black Hole Spins} \label{sec:spin_dist}

@@

Now we model each of the components' orientation distributions with independent \textsc{MSpline} models as done above, and show the inferred 
primary (orange), and secondary (olive) distributions in figure \ref{fig:ind_spintilt_dist}. The orientation distibutions do not agree quite as well as 
the magnitude distibutions did in figure \ref{fig:ind_spinmag_dist}, and the PPDs look to peak at different values, but the wide uncertainties still are 
consistent with both each other and the \textsc{Default} model's PPD. We find the two distributions to peak at: $\cos{\theta_1}=$\result{$\CIPlusMinus{\macros[MSplineIndependentCompSpins][peakCosTilt1]}$} 
and $\cos{\theta_2}=$\result{$\CIPlusMinus{\macros[MSplineIndependentCompSpins][peakCosTilt2]}$}, showing that the primary distribution peak is inferred further away 
from the assumed $\cos{\theta}=1$ with the \textsc{Default} model. There is also significant (albeit uncertain) evidence of spin mis-alignments in each distribution, finding 
the fraction of mis-aligned primary and secondary components as: $f_{1,<0}=$\result{$\CIPlusMinus{\macros[MSplineIndependentCompSpins][negFrac1]}$} andand $f_{2,<0}=$\result{$\CIPlusMinus{\macros[MSplineIndependentCompSpins][negFrac2]}$}.
We again calculate the isotropy ratio, Y, for each and find: $\log_{10}Y_1=$\result{$\CIPlusMinus{\macros[MSplineIndependentCompSpins][log10gammaFrac1]}$} and 
$\log_{10}Y_2=$\result{$\CIPlusMinus{\macros[MSplineIndependentCompSpins][log10gammaFrac2]}$}.

@@

While the component spin magnitude and tilts are more easily interpretable in context of the astrophysics, they are parameters that 
are not measured well during individual event parameter estimation. The best measured spin parameter, that enters the waveform at XXPN, is 
called the effective spin defined as: $\chi_\mathrm{eff} = \frac{a_1\cos{\theta_1} + qa_2\cos{\theta_2}}{1+q}$. As an alternative check 
on the spin distributions we also try modeling an MSpline distribution of effective spins instead of component spin magnitude and tilts 
as done above. Figure \ref{fig:chieff_dist} shows the inferred effective spin distribution with the MSpline model (red) along with the 
inferred effective spin distribution transformed from the PPDs of the component spin models shown previously. We find considerable agreement 
among the component spin distributions, highlighting that wildy different component spin distributions can imply very similar effective spin 
distributions which is the better constrained parameter. When modeling the effective spin with the \textsc{MSpline} model we see very similar 
shape, but with a slightly sharper peak centered at $\chi_\mathrm{eff}=$\result{$\CIPlusMinus{\macros[ChiEffective][chieff][PeakChiEff]}$}, compared to 
$\chi_\mathrm{eff}=$\result{$\CIPlusMinus{\macros[ChiEffective][default][PeakChiEff]}$} with the \textsc{Default} model. As for the misaligned spin question, 
we can investigate the fraction of systems with effective spins that are mis-aligned (i.e. $\chi_\mathrm{eff}<0$) and find for the \textsc{MSpline} 
model $f_{\chi_\mathrm{eff}<0}=$\result{$\CIPlusMinus{\macros[ChiEffective][chieff][FracBelow0]}$}, compared to $f_{\chi_\mathrm{eff}<0}=$\result{$\CIPlusMinus{\macros[ChiEffective][default][FracBelow0]}$} 
with the \textsc{Default} model.
